E Coli Project Paper Incredibly Rough Draft

### 2013-08-23 paper/paper.tex
paper builds correctly with figures

>>>>

 \begin{figure}
   \includegraphics[width=\columnwidth]{../data/shape-p/plots/debug-box-plot_D--p-150-60-0-0-1500}
   \caption{Protein density fluctuation with time against the polar
     wall in a 4$\mu m$ by 2$\mu m$ pill shaped cell.  The wall-bound
     proteins are shown at a point that is on the wall and the
     cytoplasm densities are shown at a point immediately adjecent.
     This plot is normalized so that every protein density peaks at 1}
   \label{frequency-plot-40-20-0-0-150}
 \end{figure}
